The paper on \Large \bf Blockchain Frontrunning

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] clean up traditional prevention methods

\emph{Blockchain front-running mitigation/prevention}. The traditional methods of preventing front-running are based on regulation and restrictions applied to the brokers and actors within the markets, such methods do not apply to blockchains, no enforcement methods, ...

>>>>

The traditional methods to prevent front-running does not apply to blockchain applications, as mainly they are based on central enforcement and limitations, also in case of blockchains the actors whom are front-running could be anonymous and the fear of lawsuits would not apply. \\
